Review questions list

### 2020-10-17 docs/revision/reply.tex
add: note to the shifted ref and figures

	We want to thank the reviewer for his keen eyes. Indeed the number of features were wrongly listed in the paper even though there were 5 features listed in that sentence. The mistake is fixed and highlighted in the revised manuscript.

@@

	Both datasets are treated separately during experiments. Input neurons of the ANN systems are adjusted depending on the dataset used in a particular experiment without altering the rest of the architecture.

@@

	Requested information is added to the respective figures.

@@

	The newly added average MSE values in the Figure 4 shows that the method in [18] is actually better at minimizing the error in these particular cases. Additionally, in the detailed performance analysis table (Table II), it is evident that the method at [18] and proposed method without the GAN phase has comparable results. However, Figure 4c shows that the error rate of both methods are accumulated differently. Even with the limited samples, the method at [18] is a good predictor of the real curve, except the shape of the curve does not actually model the real output; but a very rough estimation of it. The proposed ANN structure predicts the shape of the curve much better, however, it clearly requires more samples to fit that curve to the real output. Therefore, method at [18] cannot be refined further with less-than-ideal generated samples, on the other hand, the proposed architecture can benefit from increased number of samples. This was our aim when designing the proposed architecture. In fact, in our experiments, we have found that GAN phase has nearly no positive effect on the method proposed in [18]. We have excluded these experiments from the paper as it is already over the page limit. One last point we would like to show is that in Table II, in the SPR dataset, the reduction in error achieved by changing the network is less than 10\%, however, when GAN phase is also included, reduction reaches 68\%.

@@

	We thank the respected reviewer for catching this sentence. We believe the meaning of this sentence has been completely altered during language editing. We have fixed this mix up.

@@

	We have used the networks described in [18] as a starting point and applied changes that are known to solve the issues that are surfaced when this method is applied to a more difficult dataset. While we cannot give an exact time frame to the solution, we have spent at least several weeks adapting the ANN for this difficult problem.

@@

	We would like to thank the reviewer for noticing the missing metric in the table, it is indeed MSE. We have updated the table title to include the metric.

@@

	The requested MSEs are provided on the graphs in the new manuscript. \\

@@

	Finally, it is possible to verify the results from Fig 6c as these are two of the individual geometric configurations that the ANN systems estimated. Even though there still is a deviation from the ground truth, ANN trained with the help of augmented samples is good at estimating the location of the peak.

\end{document}

>>>>

	We want to thank the reviewer for his keen eyes. Indeed the number of features were wrongly listed in the paper even though there were 5 features listed in that sentence. The mistake is fixed and highlighted in the revised manuscript. \\
	\textbf{NB: [18] has been shifted to [13] in the revised manuscript}

@@

	Both datasets are treated separately during experiments. Input neurons of the ANN systems are adjusted depending on the dataset used in a particular experiment without altering the rest of the architecture.\\
	\textbf{NB: [18] has been shifted to [13] in the revised manuscript.}

@@

	Requested information is added to the respective figures.\\
	\textbf{NB: Fig. 4c, Fig. 6 have been shifted to Fig. 5c, Fig. 7 respectively in the revised manuscript.}

@@

	The newly added average MSE values in the Figure 4 shows that the method in [18] is actually better at minimizing the error in these particular cases. Additionally, in the detailed performance analysis table (Table II), it is evident that the method at [18] and proposed method without the GAN phase has comparable results. However, Figure 4c shows that the error rate of both methods are accumulated differently. Even with the limited samples, the method at [18] is a good predictor of the real curve, except the shape of the curve does not actually model the real output; but a very rough estimation of it. The proposed ANN structure predicts the shape of the curve much better, however, it clearly requires more samples to fit that curve to the real output. Therefore, method at [18] cannot be refined further with less-than-ideal generated samples, on the other hand, the proposed architecture can benefit from increased number of samples. This was our aim when designing the proposed architecture. In fact, in our experiments, we have found that GAN phase has nearly no positive effect on the method proposed in [18]. We have excluded these experiments from the paper as it is already over the page limit. One last point we would like to show is that in Table II, in the SPR dataset, the reduction in error achieved by changing the network is less than 10\%, however, when GAN phase is also included, reduction reaches 68\%. \\

	\textbf{NB: [18], Fig. 4c, Fig. 6 has been shifted to [13], Fig. 5c, Fig. 7 respectively in the revised manuscript.}

@@

	We thank the respected reviewer for catching this sentence. We believe the meaning of this sentence has been completely altered during language editing. We have fixed this mix up. \\
	\textbf{NB: [18] has been shifted to [13] in the revised manuscript.}

@@

	We have used the networks described in [18] as a starting point and applied changes that are known to solve the issues that are surfaced when this method is applied to a more difficult dataset. While we cannot give an exact time frame to the solution, we have spent at least several weeks adapting the ANN for this difficult problem. \\

	\textbf{NB: [18] has been shifted to [13] in the revised manuscript.}

@@

	We would like to thank the reviewer for noticing the missing metric in the table, it is indeed the MSE. We have updated the table title to include the metric.

@@

	The requested MSEs are provided on the graphs in the revised manuscript. \\

	\textbf{NB: [18], Fig. 4 has been shifted to [13], Fig. 5 respectively in the revised manuscript.}

@@

	Finally, it is possible to verify the results from Fig 6c as these are two of the individual geometric configurations that the ANN systems estimated. Even though there still is a deviation from the ground truth, ANN trained with the help of augmented samples is good at estimating the location of the peak. \\

	\textbf{NB: Fig. 6 has been shifted to Fig. 7 in the revised manuscript.}
\end{document}
